---
title: "`env` vignette"
output:
    github_document:
        toc: true
        toc_depth: 4
knit: (function(inputFile, encoding) {
      out_dir <- "../";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  collapse = TRUE,
  comment = "#")
options(width = 60)
library(cli)
library(sloop)
library(fs)
library(kableExtra)
```

`box` is loaded using [`pak`](https://pak.r-lib.org/), which checks for installation, and then loads with `pak::pkg_install()`.

```{r pak-inst, eval=FALSE, message=FALSE}
if (!requireNamespace('pak')) {
    install.packages('pak', repos = 'https://r-lib.github.io/p/pak/dev/')
}
pak::pkg_install('klmr/box@dev')
```

# module `env`

This covers the "*The hierarchy of module environments*" [vignette.](https://klmr.me/box/articles/mod-env-hierarchy.html) These modules are stored in the `env/` folder

```{r tree-env, echo=FALSE}
fs::dir_tree("env")
```
## `c`

> `c`1) defines and exports `f()`

```{r c, eval=FALSE}
# c1) defines and exports f()
#' @export
f = function() {
  "c$f"
}
```

## `b`

> 
> - `b`1) defines and exports `f()`
> 
> - `b`2) defines (but doesn't export) `g()`
> 

```{r b, eval=FALSE}
# b1) defines and exports f()
#' @export
f = function() {
  "b$f"
}

# b2) defines (but doesn't export) g()
g = function() {
  "b$g"
}
```

## `a`

> `a`1) imports and re-exports all names from `b` (changing the name of `b$f` to `g`)
> 
> `a`2) imports, but does not re-export, all names from `c`  
> 
> `a`3) additionally, defines an alias for the module, which it exports
> 

```{r a, eval=FALSE}
# a1) imports/re-exports all names from b (alias b$f as 'g')
#' @export
box::use(./b[g = f, ...]) 

# 2) imports (doesn't re-export) all names from c
box::use(./c[...]) 

# additionally, defines an alias for the module, which it exports
#' @export
box::use(./c)

#' @export
f = function() {
  "a$f"
}

f_of_c1 = c$f
f_of_c2 = get('f', parent.env(environment()))
stopifnot(identical(f_of_c1, f_of_c2))
```

> If users create a module alias in their `box::use` call, the alias will be a reference to this environment.

```{r}
box::use(a = env/a[f, g])
a
```

## Calling `c` from `a`

The `a` module is available to me as `a$c` 

```{r}
ls(a$c)
```

It's function is available as `a$c$f()`

```{r}
a$c$f()
```


## Calling `b` (as `g`) from `a` 

`b` uses the `g()` alias here, and only exported `f()`

```{r}
a$g()
```


## Calling `a` from `a` 

We can access the `f()` function from a using `a$f()`

```{r}
a$f()
```

## `f()` of `c` (1)

`f_of_c1` stores `c$f()` from `a$c$f`

```{r f_of_c1}
f_of_c1 = a$c$f
f_of_c1
```

## `f()` of `c` (2)

`f_of_c2` stores the environment of `a$f()` function

```{r}
environment()
parent.env(environment())
```

```{r f_of_c2}
f_of_c2 = get("f", pos = parent.env(environment()))
f_of_c2
```


