---
title: "`box` internals"
output: github_document
knit: (function(inputFile, encoding) {
      out_dir <- "../";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  collapse = TRUE,
  comment = "#> ")
options(width = 60)
library(tidyverse)
library(stringr)
library(cli)
library(sloop)
source("../R/utils.R")
```

Package is loaded using [`pak`](https://pak.r-lib.org/), which checks for installation, and then loads with `pak::pkg_install()`.

```{r pak-inst, eval=FALSE, message=FALSE}
if (!requireNamespace('pak')) {
    install.packages('pak', repos = 'https://r-lib.github.io/p/pak/dev/')
}
pak::pkg_install('klmr/box@dev')
```


# Internals

For this example, we'll use the example in `box/`

```{r tree-examples, echo=FALSE}
fs::dir_tree("box/")
```

## `hello_world`

Now assume we've stored the following module in `box/hello.R`:

``` r
#' @export
hello = function (name) {
    message('Hello, ', name, '!')
}

#' @export
bye = function (name) {
    message('Goodbye ', name, '!')
}
```

To use this module, we can use `box::use()` and refer to the path (unquoted)

```{r box-use}
box::use(box/hello_world)
hello_world
```

The functions are visible with `names()`

```{r names-hello_world}
names(hello_world)
```

To use the `hello()` and `bye()` functions in `box/hello_world.R`, we can use **`R script$function()`**:

```{r use-box-fun}
hello_world$hello('Martin')
hello_world$bye('Martin')
```

## What is `hello_world`?

We can use the `get_info()` function to explore it's contents:

```{r get_info}
get_info(hello_world)
```

This tells me there are multiple nested attributes in the `box$mod` class.

## `"box$mod"`

If we look at the structure of hello_world, we can see the multiple layers of attributes and classes: 

```{r str-hello_world}
str(hello_world)
```
### `"environment"` name

```{r}
environmentName(hello_world)
```

### "name"

```{r attr-hello_world-name}
attr(hello_world, "name")
```

This is a character vector 

```{r attr-hello_world-name-class}
attr(hello_world, "name") |> str()
```

### "spec"

```{r attr-hello_world-spec, eval=FALSE}
attr(hello_world, "spec")
#> mod_spec(mod(box/hello_world))
```

This is a list of five items: 3 character vectors (`name`, `prefix`, `alias`), one logical vector (`explicit`), and one `NULL` value (`attach`)

```{r attr-hello_world-spec-str}
attr(hello_world, "spec") |> str()
```

There's also a nested class in the `"spec"`

```{r attr-hello_world-spec-class}
attr(hello_world, "spec") |> class()
```

### "info"

The `"info"` attribute contains the full path to the module.

```{r attr-hello_world-info, eval=FALSE}
attr(hello_world, "info")
#> <mod_info: hello_world at /Users/mjfrigaard/projects/rbox/boxes/box/hello_world.R>
```

The `"info"` attribute is a list with two items and two classes

```{r attr-hello_world-info-str}
attr(hello_world, "info") |> str()
```
The `"info"` attribute contains two classes:

```{r attr-hello_world-info-class}
attr(hello_world, "info") |> class()
```

The `"info"` attribute list has a `'name'`

```{r attr-hello_world-info-name}
attr(hello_world, "info")['name']
```

The `"info"` attribute list also has a `'source_path'`

```{r attr-hello_world-info-source_path}
attr(hello_world, "info")['source_path']
```

### "namespace"

The namespace has an environment and three attributes (`"name"`, `"class"`, `"loading"`)

```{r hello_world-namespace}
attr(hello_world, "namespace")
```
The `"name"` of the `"namespace"` attributes is a character vector

```{r attr-hello_world-namespace-name}
attr(hello_world, "namespace") |> attr("name") |> str()
```

The `class` of the `"namespace"` attribute is `"box$ns"`

```{r attr-hello_world-namespace-class}
attr(hello_world, "namespace") |> class()
```

The `loading` attribute of the `"namespace"` attribute is a logical (`FALSE`)

```{r hello_world-namespace-loading}
attr(hello_world, "namespace") |> attr("loading") |> str()
```







